Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-07-19 response.tex

\textbf{A}: It is mentioned in the paper that there are enough samples to invert the covariance matrix. We have not done a statistical analysis in the scope of this work because we only use the partial correlation to rank pairs and therefore a statistical analysis is not really needed to make that ranking. However, it would be interesting to do it in future works.

\section*{Reviewer 2:}

\textcolor{blue}{It would be necessary to have information about the computational complexity, scalability, memory requirements, and execution time for these methods.}

\textbf{A}: We obviously agree with the reviewer that such informations are interesting, especially in the context of a challenge. For the simplified method, it only takes a few hours (about 3 to 6 hours depending on the machine used) and a few gigabytes of memory. The ``Full method'' needs the double of time (about 6 to 12 hours) and it requires a few hours more to take into account the edge directionality. GTE and GENIE3 take more time to compute than PC and they require about xx \textcolor{red}{(AS: Need AJ to know exactly the execution time)} hours and yy hours respectively. However, GENIE3 is highy parallelizable (by taking several smaller forests or applying GENIE3 on subsets of variables) and the execution time can be significantly reduced.

However, let us note that the simple method presented in the paper already gives good performances despite its light computational needs.

We also would like to mention that our code is available publicly on \url{https://github.com/asutera/kaggle-connectomics} and that some verifications, including memory requirements and execution time, of the ``Full method'' are displayed on the challenge website \url{http://connectomics.chalearn.org/home/challenge-results-verification}.\\

### 2014-07-19 article.tex
some changes and computational information deleted

\begin{figure}[t]
\centering
\subfigure[PCA]{\includegraphics[width=0.45\textwidth]{explained_variance_all} \label{fig:PCA}}
\subfigure[SVD]{\includegraphics[width=0.45\textwidth]{singular_values_all} \label{fig:SVD}}
\caption{Explained variance ratio by component (left) and singular value ratio by component (right) for all networks.}
\label{fig:pca}
\end{figure}
\section{Computational information}

To perform experiments, we used a Macbook Pro (2014) with a ram memory 16Go 1600 MHz DDR3 and a processor 2.3GHz Intel Core i7.

In order to compare the execution time with other methods, it takes about xx and xx hours to compute respectively GTE and GENIE3. However, GENIE3 is highly parallelizable (by taking several smaller forests or applying GENIE3 on subsets of variables) and the execution time can be significantly reduced.

\begin{table}[h]
\caption{Execution time, scalability, memory requirements for methods described in the paper. \textcolor{red}{to do.}}
\label{tab:results_appendix}
\centering
\small
\begin{tabular}{| l|c|c|} \hline
Methods & Execution time  & Memory requirements \\ \hline
PC & & $\sim$5Go\\
Averaging & & \\
Full Method & & \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{figure}[t]
\centering
\subfigure[PCA]{\includegraphics[width=0.45\textwidth]{explained_variance_all} \label{fig:PCA}}
\subfigure[SVD]{\includegraphics[width=0.45\textwidth]{singular_values_all} \label{fig:SVD}}
\caption{Explained variance ratio by component (left) and singular value ratio by component (right) for all networks.}
\label{fig:pca}
\end{figure}

% \section{Computational information}

% To perform experiments, we used a Macbook Pro (2014) with a ram memory 16Go 1600 MHz DDR3 and a processor 2.3GHz Intel Core i7.

% In order to compare the execution time with other methods, it takes about xx and xx hours to compute respectively GTE and GENIE3. However, GENIE3 is highly parallelizable (by taking several smaller forests or applying GENIE3 on subsets of variables) and the execution time can be significantly reduced.

% \begin{table}[h]
% \caption{Execution time, scalability, memory requirements for methods described in the paper. \textcolor{red}{to do.}}
% \label{tab:results_appendix}
% \centering
% \small
% \begin{tabular}{| l|c|c|} \hline
% Methods & Execution time  & Memory requirements \\ \hline
% PC & & $\sim$5Go\\
% Averaging & & \\
% Full Method & & \\ \hline
% \end{tabular}
% \end{table}
